---
title: "sensor"
output: html_document
http://rpubs.com/xkuang/YOYO
---
```{r}
library(tidyr, dplyr)
library(dplyr)
library(corrplot)
library(ggplot2)
library(rpart)
library(ROCR)
E1 <- read.csv("2016-12-15_12-00-32.csv", header = TRUE, stringsAsFactors = FALSE)
N1 <- read.csv("2016-12-15_12-00-36.csv", header = TRUE, stringsAsFactors = FALSE)

toSeconds <- function(x){
  if (!is.character(x)) stop("x must be a character string of the form H:M:S")
  if (length(x)<=0)return(x)
  
  unlist(
    lapply(x,
           function(i){
             i <- as.numeric(strsplit(i,':',fixed=TRUE)[[1]])
             if (length(i) == 3) 
               i[1]*3600 + i[2]*60 + i[3]
             else if (length(i) == 2) 
               i[1]*60 + i[2]
             else if (length(i) == 1) 
               i[1]
           }  
    )  
  )  
} 
#code function reference: http://stackoverflow.com/questions/10835908/is-there-a-way-to-convert-mmss-00-to-seconds-00-in-r
N1$Time <- toSeconds(N1$loggingTime)
E1$Time <- toSeconds(E1$loggingTime)

N2 <- dplyr::select(N1, Time,locationAltitude,locationSpeed,accelerometerAccelerationX,accelerometerAccelerationY,+
                      accelerometerAccelerationZ,gyroRotationX,gyroRotationY,gyroRotationZ,+
                      motionYaw,motionRoll,motionPitch,motionRotationRateX,motionRotationRateY,motionRotationRateZ,+
                      motionUserAccelerationX,motionUserAccelerationY,motionUserAccelerationZ,motionQuaternionX,+
                      motionQuaternionY,motionQuaternionZ,motionQuaternionW,motionGravityX,motionGravityY,motionGravityZ,+
                      motionMagneticFieldX,motionMagneticFieldY,motionMagneticFieldZ)

N3 <- tidyr::gather(N2,Time)
names(N3) <- c("time","variable","value")
ggplot(N3)+ geom_line(aes(x=time, y=value))+facet_wrap(~variable, scales = "free")

```



```{r}
E2 <- dplyr::select(E1, Time,locationAltitude,locationSpeed,accelerometerAccelerationX,accelerometerAccelerationY,+
                      accelerometerAccelerationZ,gyroRotationX,gyroRotationY,gyroRotationZ,motionYaw,+
                      motionRoll,motionPitch,motionRotationRateX,motionRotationRateY,motionRotationRateZ,motionUserAccelerationX,+
                      motionUserAccelerationY,motionUserAccelerationZ,motionQuaternionX,motionQuaternionY,motionQuaternionZ,+
                      motionQuaternionW,motionGravityX,motionGravityY,motionGravityZ,motionMagneticFieldX,motionMagneticFieldY,+
                      motionMagneticFieldZ)

E3 <- tidyr::gather(E2,Time)
names(E3) <- c("time","variable","value")
ggplot(E3)+ geom_line(aes(x=time, y=value))+facet_wrap(~variable, scales = "free")

```


```{r}
E3$name <- "expert"
N3$name <- "naive"
names(E3) <- c("time","variable","value","name")
names(N3) <- c("time","variable","value","name")
D1 <- dplyr::bind_rows(N3, E3)

ggplot(D1)+ geom_line(aes(x=time, y=value,color=name))+facet_wrap(~variable, scales = "free")

```


```{r pressure, echo=FALSE}
E2$name <- "expert"
N2$name <- "naive"
D <- dplyr::bind_rows(N2, E2)
D$name<-ifelse(D$name=="naive",0,1)
D <- as.data.frame(D)

COR <- cor(D)
corrplot(COR, order="AOE", method="circle", tl.pos="lt", type="upper",        
         tl.col="black", tl.cex=0.6, tl.srt=45, 
         addCoef.col="black", addCoefasPercent = TRUE,
         sig.level=0.01, insig = "blank")
```

```{r}
#pairs(D)
```
#Xiaoting's prediction model1: motionQuaternionZ(.98), motionQuaternionW(.96), motionQuaternionX(-.75)
```{r}
c.tree1 <- rpart(name ~ motionQuaternionZ + motionQuaternionW + motionQuaternionX, method="class", data=D,control=rpart.control(minsplit = 1, minbucket = 1, cp = 0.001))
#Plot and generate a CP table for your tree 
post(c.tree1, file = "tree1.ps", title = "tree1")
printcp(c.tree1)
```
Since we were using two sensors of different phones for motion recording, this experiment might contain threats of internal validity due to instrumentation (looking at the graphs of motionQuaternionZ, motionQuaternionW and motionYaw, they might not be good variables to predict expect level)

#Xiaoting's prediction model2: motionQuaternionX(-.75), motionQuaternionY(0.67), motionGravityZ(-0.45)
```{r}
c.tree2 <- rpart(name ~ motionQuaternionY + motionQuaternionX + motionGravityZ, method="class", data=D,control=rpart.control(minsplit = 1, minbucket = 1, cp = 0.001))
#Plot and generate a CP table for your tree 
post(c.tree2, file = "tree2.ps", title = "tree2")
printcp(c.tree2)
```

```{r}
D$pred <- predict(c.tree2, type = "prob")[,2]
#Now you can generate the ROC curve for your model. You will need to install the package ROCR to do this.
#Plot the curve
pred1 <- prediction(D$pred, D$name) 
plot(performance(pred1, "tpr", "fpr"),colorize=TRUE)
abline(0, 1, lty = 2)
#Calculate the Area Under the Curve
AUC1 <- unlist(slot(performance(pred1,"auc"), "y.values"))#Unlist liberates the AUC value from the "performance" object created by ROCR
#[1] 0.9931463

#Model2: from ROC1, we can set the optimal threshold.pred1 as 0.58
threshold.pred1 = 0.58
D$threshold.pred1 <- ifelse(D$pred <= threshold.pred1, "0 r","1 r") 
#Now generate three diagnostics:
table1 <- table(D$name, D$threshold.pred1)
table1
#     0    1
#0 1930    31
#1   15  1138
accuracy1 <- (1930+1138)/(1930+1138+31+15) # [1] 0.985228
precision1 <- 1138/(1138+31) #[1] 0.9734816
recall1 <- 1138/(1138+15) #[1] 0.9869905
```
#Xiaoyue's prediction model3: motionQuaternionX,accelerometerAccelerationX and motionPitch
```{r}
c.tree3 <- rpart(name ~ motionQuaternionX + accelerometerAccelerationX + motionPitch, method="class", data=D,control=rpart.control(minsplit = 1, minbucket = 1, cp = 0.001))
#Plot and generate a CP table for your tree 
post(c.tree3, file = "tree3.ps", title = "tree3")
printcp(c.tree3)

D$pred2 <- predict(c.tree3, type = "prob")[,2]
#Now you can generate the ROC curve for your model. You will need to install the package ROCR to do this.
#Plot the curve
pred2 <- prediction(D$pred2, D$name) 
plot(performance(pred2, "tpr", "fpr"),colorize=TRUE)
abline(0, 1, lty = 2)
#Calculate the Area Under the Curve
AUC2 <-unlist(slot(performance(pred2,"auc"), "y.values"))#Unlist liberates the AUC value from the "performance" object created by ROCR
#[1] 0.9992698

#Model3: from ROC2, we can set the optimal threshold.pred1 as 0.7
threshold.pred2 = 0.7
D$threshold.pred2 <- ifelse(D$pred2 <= threshold.pred2, "0 r","1 r") 
#Now generate three diagnostics:
table2 <- table(D$name, D$threshold.pred2)
table2
#   0 r  1 r
#0 1950   11
#1    2 1151
accuracy2 <- (1950+1151)/(1950+1151+11+2) # [1] 0.9958253
precision2 <- 1151/(1151+11) #[1] 0.9905336
recall2 <- 1151/(1151+2) #[1] 0.9982654
```
#Jiaxi's prediction model4: accelerometerAccelerationY, motionpitch and motionQuaternionY
```{r}
c.tree4 <- rpart(name ~ accelerometerAccelerationY + motionPitch + motionQuaternionY, method="class", data=D,control=rpart.control(minsplit = 1, minbucket = 1, cp = 0.001))
#Plot and generate a CP table for your tree 
post(c.tree4, file = "tree4.ps", title = "tree4")
printcp(c.tree4)

D$pred3 <- predict(c.tree4, type = "prob")[,2]
#Now you can generate the ROC curve for your model. You will need to install the package ROCR to do this.
#Plot the curve
pred3 <- prediction(D$pred3, D$name) 
plot(performance(pred3, "tpr", "fpr"),colorize=TRUE)
abline(0, 1, lty = 2)
#Calculate the Area Under the Curve
AUC3 <- unlist(slot(performance(pred3,"auc"), "y.values"))#Unlist liberates the AUC value from the "performance" object created by ROCR
#[1] 0.9988828

#Model4: from ROC3, we can set the optimal threshold.pred1 as 0.7
threshold.pred3 = 0.4
D$threshold.pred3 <- ifelse(D$pred3 <= threshold.pred3, "0 r","1 r") 
#Now generate three diagnostics:
table3 <- table(D$name, D$threshold.pred3)
table3
#   0 r  1 r
#0 1955    6
#1    7 1146
accuracy3 <- (1955+1146)/(1955+1146+6+7) # [1] 0.9958253
precision3 <- 1146/(1146+6) #[1] 0.9947917
recall3 <- 1146/(1146+7) #[1] 0.9939289
```
##Summary: Model Comparison

```{r}
ModelCompare = matrix(c(AUC1, accuracy1,precision1,recall1,AUC2, accuracy2,precision2,recall2, AUC3, accuracy3,precision3,recall3),nrow=4,ncol=3) 
ModelCompare <- t(ModelCompare)
ModelCompare <- as.data.frame(ModelCompare)
names(ModelCompare) <- c("AUC", "accuracy","precision","recall")
ModelCompare
```

#1. Xiaoting's model 2.Xiaoyue's model (best in recall, most accurate according to AUC) 3. Jiaxi's model(best in precision)







